The Shape and <span style='color: #b70000'>Co</span><span style='color: #00AEF3'>lor</span> of Politics

### 2023-11-05 chapter_2/src/slides/color-book.qmd
update slides

A key takeaway is that we are being pushed to react to information to before we even realize it.
::::

@@

- Presents a cognitive model that builds upon existing info. processing models to consider pre-conscious influences.
    - All of these steps happen <span style='color: #b70000'>bef</span><span style='color: #00aef3'>ore</span> the pre-existing info. processing models
:::

@@

Campaigns use the colors more or less <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> depending on partisan composition of electoral district

@@

- <span style="color: #616A6B">How do colors convey political information and effect individual attitudes? </span>
- How do colors influence political deliberation?
- How do colors influence neighborhood evaluations?

@@

names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
modelsummary(
  list_fitted[["h_5"]]
  , stat = "conf.int"
  , conf_level = 0.9
  , metrics = c("n.obs", "RMSE")
  , coef_map = c(
    "b_dem_vote_share" = "Democratic vote share (percent)"
    , "b_Intercept" = "Intercept"
  )
  , notes = c(
    "Data source: Center for Political Design and MIT Election Lab"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE

>>>>

A key takeaway is that we are being pushed to react to information before we even realize it.
::::

@@

- Presents a cognitive model that builds upon existing info. processing models to consider pre-conscious influences.
    - All of these steps happen <span style='color: #b70000'>be</span><span style='color: #00aef3'>fore</span> the pre-existing info. processing models
:::

@@

Campaigns use the colors <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> more or less depending on partisan composition of electoral district

@@

- <span style="color: #616A6B">How do colors convey political information and affect individual attitudes? </span>
- How do colors influence political deliberation?
- How do colors influence neighborhood evaluations?

@@

list_fitted[["h_5"]] <- list(
    list_fitted[["h_5"]][["red"]]
    , list_fitted[["h_5"]][["blue"]]
)
names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
modelsummary(
  list_fitted[["h_5"]]
  , stat = "conf.int"
  , conf_level = 0.9
  , metrics = c("n.obs", "RMSE")
  , coef_map = c(
    "b_dem_vote_share" = "Democratic vote share (percent)"
    , "b_Intercept" = "Intercept"
  )
  , notes = c(
    "Data source: Center for Political Design and MIT Election Lab"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
